\chapter{Introduction}
\section{Problem Statement}
To develop a software application that will help educators to grade students fairly based on rubrics. Rubrics are generally something that makes the life of an educator easier. Rather than adding an arbitrary grade to an assignment, with rubrics educators are able to determine exactly where a student’s work excelled beyond expectations and exactly where it lacked quality. Our software will provide a platform for the educators in which they would be able to create a grading rubric. The educator would define performance levels (like excellent, good, average, poor etc.) and parameters (like neatness, proper content etc.) for grading. Each performance level would have some weight assigned to it based on which
the software would calculate the student’s final score. This software will also provide a proper feedback to the students and will tell them what areas they need to work on based on their assignment submissions.\\
\section{Scope of the Project}\
Rubrics system provides a web-based and mobile-based platform to students as  well as the grader, where students can upload their work and the grader will evaluate their work according to the designed metric developed by the grader. This system displays all the performance of the student in a graphical format so that student will get the clear idea about where he/she is good or where he/she is lagging and what is pending jobs and what is completely done.Using Rubrics system, the grader can review the students work as well as give proper feedback to the student and get the personal attention from the grader.\\
\section{Current Scenario}
Currently there are four such student evaluation tools available online. The following table gives a brief list of their included features.
\begin {table}[H]
\begin{center}
\begin{tabular}{ | m{3.5cm} | m{2cm}| m{2cm}| m{2cm} |m{2.6cm}| m{2cm} | }
\hline
\textbf{Features} & \textbf{RubiStar} & \textbf{Moodle} & \textbf{iRubric} & \textbf{EssayTagger} & \textbf{Rubric System}\\ 
\hline
Multiple Templates & Yes & No & No & No & Yes\\
\hline
Dyanamic Create Templates & Yes & Yes & Yes & No & Yes\\
\hline
Graphical Performance Analysis & No & Yes & No & No & Yes\\
\hline
User Convenient & Yes & No & No & Yes & Yes\\
\hline
Pricing & Yes & Yes & Yes & Yes & No\\
\hline
Feeback to students & No & Yes & Yes & Yes & Yes\\
\hline
\end{tabular}\\
\caption {Current Scenario}
\end{center}
\end {table}


\section{Need for the Proposed System}
\begin{itemize}
\item To evaluate the quality of students.
\item To focus on measuring objectives(performance, behavior, and quality).
\item To develop a better way of communication between teachers and students.
\item To increase interest in ``performance-based education".
\end{itemize}
\section{Summary of the Results / Task completed }
\begin{itemize}
\item Developed a web-Prototype and Mobile Application Prototype
\item Did literature survey of various evaluation systems
\item Started Web and Android Application implementation(Coding)
\end{itemize}
\newpage

